

\bibitem{Chang:ICCAD14}
N.~Chang, D.~Baek, and J.~Hong, ``Power consumption characterization, modeling
  and estimation of electric vehicles,'' in Proceedings of IEEE/ACM
  International Conference on Computer-Aided Design, 2014.

\bibitem{Park:DAC13}
S.~Park, Y.~Kim, and N.~Chang, ``Hybrid energy storage systems and battery
  management for electric vehicles,'' in Proceedings of IEEE/ACM Design
  Automation Conference, 2013.

\bibitem{Nissan:SAE11}
``2011 nissan leaf vehicle overview.'' SAE Vehicle Electrification, 2011.

\bibitem{Grebe:ATZ11}
U.~D. Grebe and L.~T. Nitz, ``Voltec – the propulsion system for chevrolet
  volt and opel ampera,'' 2011.

\bibitem{Vaz:JPS14}
W.~Vaz, A.~K. Nandi, R.~G. Landers, and U.~O. Koylu, ``Electric vehicle range
  prediction for constant speed trip using multi-objective optimization,'' 
  Journal of Power Sources, 2014.

\bibitem{Lin:CCA14}
X.~Lin, D.~Gorges, , and S.~Liu, ``Eco-driving assistance system for electric
  vehicles based on speed profile optimization,'' in Proceedings of IEEE
  Conference on Control Applications, 2014.

\bibitem{Oliva:PHM13}
J.~A. Oliva, C.~Weihrauch, and T.~Bertram, ``A model-based approach for
  predicting the remaining driving range in electric vehicles,'' in 
  Proceedings of Conference of the Prognostics and Health Management Society,
  2013.

\bibitem{Kachroudi:TVT12}
S.~Kachroudi, M.~Grossard, and N.~Abroug, ``Predictive driving guidance of full
  electric vehicles using particle swarm optimization,'' Ieee Transactions
  On Vehicular Technology, 2012.

\bibitem{Dib:OGST12}
W.~Dib, A.~Chasse, D.~di~Domenico, P.~Moulin, and A.~Sciarretta, ``Evaluation
  of the energy efficiency of a fleet of electric vehicle for eco-driving
  application,'' Oil Gas Science and Technology, 2012.

\bibitem{Schwickart:JFI15}
T.~Schwickart, H.~Voos, J.-R. Hadji-Minaglou, M.~Darouach, and A.~Rosich,
  ``Design and simulation of a real-time implementable energy-efficient
  model-predictive cruise controller for electric vehicles,'' Journal of
  Franklin Institute, 2015.

\bibitem{Hong:ASPDAC16}
J.~Hong, S.~Park, and N.~Chang, ``Accurate remaining range estimation for
  electric vehicles,'' in Proceedings of Asia and South Pacific Design
  Automation and Conference, 2016.

\bibitem{Wu:TR15}
X.~Wu, D.~Freese, A.~Cabrera, and W.~A. Kitch, ``Electric vehicles’ energy
  consumption measurement and estimation,'' Transportation Research Part
  D: Transport and Environment, vol. 34, 2015.

\bibitem{Kamal:TITS11}
M.~A.~S. Kamal, M.~Mukai, J.~Murata, and T.~Kawabe, ``Ecological vehicle
  control on roads with up-down slopes,'' IEEE Transactions on Intelligent
  Transportation Systems, vol. 12, no. 3, Sept., 2011.

\bibitem{Ozatay:IFAC14}
E.~Ozatay, U.~Ozguner, J.~Michelini, and D.~Filev, ``Analytical solution to the
  minimum energy consumption based velocity profile optimization problem with
  variable road grade,'' in Proceedings of IFAC world congress, 2014.

\bibitem{Ozatay:TITS14}
E.~Ozatay, S.~Onori, J.~Wollaeger, U.~Ozguner, G.~Rizzoni, D.~Filev,
  J.~Michelini, and S.~Cairano, ``Cloud-based velocity profile optimization for
  everyday driving: a dynamic-programming-based solution,'' IEEE
  Transactions on Intelligent Transportation Systems, 2014.

\bibitem{Khayyam:ESA12}
H.~Khayyam, S.~Nahavandi, and S.~Davis, ``Adaptive cruise control look-ahead
  system for energy management of vehicles,'' Expert Systems with
  Applications, 2012.

\bibitem{Yan:NAPS14}
Q.~Yan, B.~Zhang, and M.~Kezunovic, ``Optimization of electric vehicle movement
  for efficient energy consumption,'' in North American Power Symposium
  (NAPS), 2014.

\bibitem{Dib:CEP14}
W.~Dib, A.~Chasse, P.~Moulin, A.~Sciarretta, and G.~Corde, ``Optimal energy
  management for an electric vehicle in eco-driving applications,'' 
  Control Engineering Practice, 2014.

\bibitem{Dib:IVPPC11}
W.~Dib, L.~Serrao, and A.~Sciarretta, ``Optimal control to minimize trip time
  and energy consumption in electric vehicles,'' in Proceedings of IEEE
  Vehicle Power and Propulsion Conference, 2011.

\bibitem{Mensing:TR13}
F.~Mensing, E.~Bideaux, R.~Trigui, , and H.~Tattegrain, ``Trajectory
  optimization for eco-driving taking into account traffic constraints,'' 
  Transportation Research Part D: Transport and Environment, 2013.

\bibitem{Dovgana:ASC14}
E.~Dovgana, M.~Javorskib, T.~Tusara, M.~Gamsa, and B.~Filipica, ``Discovering
  driving strategies with a multiobjective optimization algorithm,'' 
  Applied Soft computing, 2014.

\bibitem{Lim:TVT17}
H.~Lim, W.~Su, and C.~C. Mi, ``Distance-based ecological driving scheme using a
  two-stage hierarchy for long-term optimization and short-term adaptation,''
  IEEE Transactions on Vehicular Technology, 2017.

\bibitem{Mandava:ITSC09}
S.~Mandava, K.~Boriboonsomsin, and M.~Barth, ``Arterial velocity planning based
  on traffic signal information under light traffic conditions,'' in 
  Proceedings of IEEE International Conference on Intelligent Transportation
  Systems, 2009.

\bibitem{Asadi:TCST11}
B.~Asadi and A.~Vahidi, ``Predictive cruise control: Utilizing upcoming traffic
  signal information for improving fuel economy and reducing trip time,'' 
  IEEE Transactions on Control Systems Technology, 2011.

\bibitem{Ozatay:CDC13}
E.~Ozatay, U.~Ozguner, D.~Filev, and J.~Michelini, ``Analytical and numerical
  solutions for energy minimization of road vehicles with the existence of
  multiple traffic lights,'' in Proceedings of IEEE International
  Conference on Decision and Control, 2013.

\bibitem{Nunzio:JRNC15}
G.~Nunzio, C.~Wit, P.~Moulin, and D.~Domenico, ``Eco-driving in urban traffic
  networks using traffic signals information,'' International Journal of
  Robust and Nonlinear Control, 2015.

\bibitem{Wu:ITS15}
X.~Wu, X.~He, and G.~Yu, ``Energy-optimal speed control for electric vehicles
  on signalized arterials,'' IEEE Transactions on Intelligent
  Transportation Systems, 2015.

\bibitem{Butler:TVT99}
K.~L. Butler, M.~Ehsani, and P.~Kamath, ``A matlab-based modeling and
  simulation package for electric and hybrid electric vehicle design,''
  IEEE Transactions on Vehicular Technology, 1999.

\bibitem{Markel:JPS02}
T.~Markel, A.~Brooker, T.~Hendricks, V.~Johnson, and K.~Kelly, ``Advisor: a
  systems analysis tool for advanced vehicle modeling,'' Journal of Power
  Sources, 2002.

\bibitem{Gao:TIE10}
Y.~Gao and M.~Ehsani, ``Design and control methodology of plug-in hybrid
  electric vehicles,'' IEEE Transactions on Industrial Electronics, 2010.

\bibitem{Song:AE14}
Z.~Song, J.~Li, X.~Han, L.~Xu, L.~Lu, M.~Ouyang, and H.~Hofmann,
  ``Multi-objective optimization of a semi-active battery/supercapacitor energy
  storage system for electric vehicles,'' Applied Energy, 2014.

\bibitem{Yin:ITEC-AP14}
Q.~Yin, Z.~Wu, and X.~Rui, ``Parameter design and optimization of electric
  vehicle,'' in Proceedings of IEEE International Transportation
  Electrification Conference and EXPO Asia-Pacific, 2014.

\bibitem{Pozo:AMAA15}
J.~B. A.~G. Alberto Fraile~del Pozo, Emilio Larrode~Pellicer and A.~Torne,
  ``Influence of the design parameters of electric vehicles in the optimization
  of energy efficiency in urban routes,'' Advanced Microsystems for
  Automotive Applications, 2015.

\bibitem{Hasanzadeh:INDEL14}
A.~Hasanzadeh, B.~Asaei, and A.~Emadi, ``Optimum design of series hybrid
  electric buses by genetic algorithm,'' in Proceedings of IEEE
  International Symposium on Industrial Electronics, 2014.

\bibitem{Ribau:AE14}
J.~P. Ribau, C.~M. Silva, and J.~M. Sousa, ``Efficiency, cost and life cycle
  co2 optimization of fuel cell hybrid and plug-in hybrid urban buses,''
  Applied Energy, 2014.
  
\bibitem{Sarre:JPS04}
G. Sarre, P. Blanchard, and M. Broussely, ``Aging of lithium-ion batteries,''
  Journal of Power Sources, 2004.
  
\bibitem{Keil:PHD17}
P. Keil, ``Aging of Lithium-Ion Batteries in Electric Vehicles,'' PhD thesis, Technische Universitat Munchen, 2017.  

