

\bibitem{ZS_millner}
Alan Millner, ``Modeling lithium ion battery degradation in electric vehicles.'' Innovative Technologies for an Efficient and Reliable Electricity Supply (CITRES), 2010 IEEE Conference on. IEEE, 2010.

\bibitem{ZS_Ning}
Gang Ning, Ralph E. White and Branko N. Popov. ``A generalized cycle life model of rechargeable Li-ion batteries.'' Electrochimica acta 51.10 (2006): 2012-2022.

\bibitem{ZS_dubarry}
Matthieu Dubarry et al. ``Capacity loss in rechargeable lithium cells during cycle life testing: The importance of determining state-of-charge.'' Journal of Power Sources 174.2 (2007): 1121-1125.

\bibitem{ZS_jean}
Jean Paul Cun, Jean No Fiorina, Michael Fraisse, And Henri Mabboux, ``The Experience of a
UPS Company in Advanced Battery Monitoring'',
MGE UPS Systems, Grenoble, France,'http://wwwmerlingerin.eunet.fr/news/techpap/tp02us.ht'

\bibitem{ZS_jayne}
M.G. Jayne and  C. Morgan, ``A New
Mathematical Model of a Lead Acid Battery for
Electric Vehicles'', Eighth Int'l Electric Vehicle


\bibitem{ZS_sims}
R.I. Sims, J.C. Carnes, M.A. Dzieciuch and
J.E. Fenton, ``Computer Modeling of Automotive
Lead Acid Batteries'', Ford Research Laboratories
Technical Report SR-90- 154, Sept., 25, I990

\bibitem{ZS_gig}
R. Giglioli, A. Buonarota, P. Menga, and M. Ceraolo, ``Charge and Discharge Fourth
Order Dynamic Model of the Lead Battery'', 10th Int'l
Electric Vehicle Symposium, Hong Kong, 1990, p. 1-9.

\bibitem{ZS_rob}
T. Robbins and J. Hawkins ``Battery model for
Overcurrent Protection Simulation of DC Distribution Systems'', INTELEC 16th
International Telecommunications Energy
Conference, p307--14, 1994.

\bibitem{ZS_zi}
Ziyad M. Salameh, Margaret A. Casacca and William
A. Lynch, ``A Mathematical Model for Lead-Acid
Batteries'', IEEE Trans. on Energy Conversion. Vol. 7,
No. 1, March 1992

\bibitem{ZS_mar}
Margaret A. Casacca and Ziyad M. Salameh,
``Determination of Lead-Acid Battery Capacity
Via Mathematical Modeling Techniques'', IEEE
Trans. on Energy Conversion. Vol. 7, No. 3, Sept.
1992

\bibitem{ZS_chan}
H. L. Chan ``A new battery model for use with battery energy storage systems and electric vehicles power systems.'' Power Engineering Society Winter Meeting, 2000. IEEE. Vol. 1. IEEE, 2000.


\bibitem{ZS_den}
D. W. Dennis, V. S. Battaglia, and A. Belanger, ``Electrochemical
modeling of lithium polymer batteries,” J. Power Sources, vol. 110,
no. 2, pp. 310-320, 2002.

\bibitem{ZS_chen}
M. Chen and G. A. Rincon-Mora, ``Accurate electrical battery model
capable of predicting runtime and I-V performance,” IEEE Trans.
Energy Conversion, vol. 21m no. 2, pp. 504-511. Jun. 2006.

\bibitem{ZS_kro}
Kroeze, Ryan C., and Philip T. Krein. ``Electrical battery model for use in dynamic electric vehicle simulations.'' Power Electronics Specialists Conference, 2008. PESC 2008. IEEE. IEEE, 2008.

%\bibitem{ZS_bai}
%Baisden, Andrew C., and Ali Emadi. ''ADVISOR-based model of a battery and an ultra-capacitor energy source for hybrid electric vehicles.'' IEEE transactions on vehicular technology 53.1 (2004): 199-205.

\bibitem{ZS_log}
D. L. Logue and P. T. Krein, ``Dynamic hybrid electric vehicle
simulation, version 1.0,” University of Illinois, Technical Report
UILUENG-98-0409, December 1998.

\bibitem{ZS_amr}
M. Amrhein and P. T. Krein, ``Dynamic simulation for analysis of
hybrid electric vehicle system and subsystem interactions, including
power electronics,” IEEE Trans. Vehicular Tech., vol. 54, no. 3, pp.
825-836, May 2005.

\bibitem{ZS_wip}
K. B. Wipke, M. R. Cuddy, and S. D. Burch, ``ADVISOR 2.1: A
user-friendly advanced powertrain simulation using a combined backward/forward
approach,

\bibitem{ZS_adv}
The ADVISOR Code and Manual are Available from the National Renewable
Energy Lab. [Online]. Available: http://www.ctts.nrel.gov/analysis

\bibitem{ZS_col}
G. Cole, ``Simple electric vehicle simulation (SIMPLEV) v3.1,” DOE
Idaho National Eng. Lab.

\bibitem{ZS_bun}
D. L. Buntin and J. W. Howze, ``A switching logic controller for a
hybrid electric/ICE vehicle,” in Proc. American Control Conf., Seattle,
WA, June 1995, pp. 1169–1175.

\bibitem{ZS_ste}
K. M. Stevens, ``A versatile computer model for the design and analysis
of electric and hybrid drive trains,” Master’s thesis, Texas A and M Univ.,
College Station, 1996.

\bibitem{ZS_but}
K. L. Butler, K. M. Stevens, and M. Ehsani, ``A versatile computer
simulation tool for design and analysis of electric and hybrid drive
trains,” in 1997 SAE Proc. Electric and Hybrid Vehicle Design Studies,
Detroit, MI, Feb. 1997, pp. 19–25.

%\bibitem{ZS_meh}
%Butler, Karen L., Mehrdad Ehsani, and Preyas Kamath. ''A Matlab-based modeling and simulation package for electric and hybrid electric vehicle design.'' IEEE Transactions on vehicular technology 48.6 (1999): 1770-1778.

\bibitem{ZS_wal}
W. W. Marr and W. J. Walsh, ``Life-cycle cost evaluations of electric/
hybrid vehicles,” Energy Conversion Management, vol. 33, no. 9,
pp. 849–853, 1992.

\bibitem{ZS_bum}
J. R. Bumby et al., ``Computer modeling of the automotive energy requirements
for internal combustion engine and battery electric-powered
vehicles,” Proc. Inst. Elect. Eng., vol. 132, pt. A, no. 5, pp. 265–279,
1985.

\bibitem{ZS_noo}
R. Noons, J. Swann, and A. Green, ``The use of simulation software
to assess advanced powertrains and new technology vehicles,” in Proc.
Electric Vehicle Symp. 15, Brussels, Belgium, Oct. 1998.

\bibitem{ZS_aue}
B. Auert, C. Cheny, B. Raison, and A. Berthon, ``Software tool for the
simulation of the electromechanical behavior of a hybrid vehicle,” in
Proc. Electric Vehicle Symp. 15, Brussels, Belgium, Oct. 1998.

\bibitem{ZS_kri}
C. Kricke and S. Hagel, ``A hybrid electric vehicle simulation model
for component design and energy management optimization,” in Proc.
FISITA World Automotive Congress, Paris, France, Sept. 1998.

\bibitem{ZS_lu}
Lu, Languang, et al., ``A review on the key issues for lithium-ion battery management in electric vehicles.'' Journal of power sources 226 (2013): 272-288.

\bibitem{ZS_bha}
Bhangu, Bikramjit S., et al., ``Nonlinear observers for predicting state-of-charge and state-of-health of lead-acid batteries for hybrid-electric vehicles.'' IEEE transactions on vehicular technology 54.3 (2005): 783-794.

\bibitem{ZS_pil}
Piller, Sabine, Marion Perrin, and Andreas Jossen., ``Methods for state-of-charge determination and their applications.'' Journal of power sources 96.1 (2001): 113-120.

\bibitem{ZS_cau}
O. Caumont, Ph. Le Moigne, P. Lenain, and C. Rombaut, ``An optimized
state of charge algorithm for lead-acid batteries in electric vehicles,” in
Electric Vehicle Symp. , vol. EVS-15, Brussels, Belgium, Sep-Oct. 30–3,
1998. Proceedings on CD-ROM

\bibitem{ZS_cun}
A. B. da Cunha, B. R. de Almeida, and D. C. da SilvaJr., ``Remainingcapacity  measurement  and  analysis  of  alkaline  batteries  for  wirelesssensor nodes,”IEEE Transactions on Instrumentation and Measurement,vol. 58, no. 6, pp. 1816–1822, June 2009.


\bibitem{ZS_yu}
Yu, Jianbo. ``State-of-health monitoring and prediction of lithium-ion battery using probabilistic indication and state-space model.'' IEEE Transactions on Instrumentation and Measurement 64.11 (2015): 2937-2949.

\bibitem{ZS_pas}
P. E. Pascoe and A. H. Anbuky, ``Standby power system VRLA battery
reserve life estimation scheme,” IEEE Trans. Energy Convers., vol. 20,
no. 4, pp. 887–895, Dec. 2005.

\bibitem{ZS_ver}
M.  Verbrugge  and  E.  Tate,  ``Adaptive  state  of  charge  algorithm  for nickel metal hydride batteries including hysteresis phenomena,”Journal of Power Sources, vol. 126, no. 1, pp. 236–249, 2004.

\bibitem{ZS_sin}
 P. Singh, C. Fennie, D. Reisner, and A. Salkind, ``A fuzzy logic approach to  state-of-charge  determination  in  high  performance  batteries  with applications  to  electric  vehicles,”  in15th  Electric  Vehicle  Symposium,vol. 15, 1998, pp. 30–35.

\bibitem{ZS_ang}
  C. Chan, E. Lo, and S. Weixiang, ``The available capacity computation model  based  on  artificial  neural  network  for  lead–acid  batteries  in electric vehicles,”Journal of Power Sources, vol. 87, no. 1, pp. 201–204,2000.

\bibitem{ZS_11}
 Y.  Lee,  W.  Wang,  and  T.  Kuo,  ``Soft  computing  for  battery  state-of-charge (bsoc) estimation in battery string systems,”IEEE Transactionson Industrial Electronics,, vol. 55, no. 1, pp. 229–239, 2008.

\bibitem{ZS_12}
 P.  Pascoe  and  A.  Anbuky,  ``Vrla  battery  discharge  reserve  time  estimation,”Power  Electronics,  IEEE  Transactions  on,  vol.  19,  no.  6,  pp.1515–1522, 2004.

\bibitem{ZS_13}
 I. Kim, ``Nonlinear state of charge estimator for hybrid electric vehicl ebattery,”IEEE  Transactions  on  Power  Electronics,,  vol.  23,  no.  4,  pp.2027–2034, 2008.

\bibitem{ZS_14}
 Y. He, W. Liu, and B. Koch, ``Battery algorithm verification and development using hardware-in-the-loop testing,”Journal of Power Sources,vol. 195, no. 9, pp. 2969–2974, 2010.

\bibitem{ZS_15}
 G.  Plett,  ``Extended  kalman  filtering  for  battery  management  systems of lipb-based hev battery packs: Part 1. background,”Journal of power sources, vol. 134, no. 2, pp. 262–276, 2004.

\bibitem{ZS_16}
G. Plett, ``Extended  kalman  filtering  for  battery  management  systems  of lipb-based  hev  battery  packs:  Part  2.  modeling  and  identification,”Journal of power sources, vol. 134, no. 2, pp. 262–276, 2004. 

\bibitem{ZS_17}
G. Plett, ``Extended  kalman  filtering  for  battery  management  systems  of lipb-based  hev  battery  packs:  Part  3.  state  and  parameter  estimation,”Journal of power sources, vol. 134, no. 2, pp. 277–292, 2004.

\bibitem{ZS_18}
 G. Dong, J. Wei, and Z. Chen, ``Kalman filter for onboard state of charge estimation and peak power capability analysis of lithium-ion batteries,”Journal of Power Sources, vol. 328, pp. 615–626, 2016.

\bibitem{ZS_19}
Z.  Chen,  Y.  Fu,  and  C.  Mi,  ``State  of  charge  estimation  of  lithium-ionbatteries in electric drive vehicles using extended kalman filtering,”IEEETransactions  on  Vehicular  Technology,,  vol.  62,  no.  3,  pp.  1020–1030, 2013.

\bibitem{ZS_20}
 G.  Dong,  J.  Wei,  C.  Zhang,  and  Z.  Chen,  ``Online  state  of  chargeestimation  and  open  circuit  voltage  hysteresis  modeling  of  lifepo  4battery  using  invariant  imbedding  method,”Applied  Energy,  vol.  162,pp. 163–171, 2016.

\bibitem{ZS_21}
  X. Tang, Y. Wang, and Z. Chen, ``A method for state-of-charge estimationof lifepo 4 batteries based  on a dual-circuit state observer,”Journal ofPower Sources, vol. 296, pp. 23–29, 2015.

\bibitem{ZS_22}
  Y.  Wang,  C.  Zhang,  and  Z.  Chen,  ``A  method  for  state-of-chargeestimation  of  lifepo  4  batteries  at  dynamic  currents  and  temperaturesusing particle filter,”Journal of power sources, vol. 279, pp. 306–311, 2015.

\bibitem{ZS_23}
  X.  Liu,  J.  Wu,  C.  Zhang,  and  Z.  Chen,  ``A  method  for  state  ofenergy  estimation  of  lithium-ion  batteries  at  dynamic  currents  andtemperatures,”Journal of Power Sources, vol. 270, pp. 151–157, 2014.

\bibitem{ZS_24}
  L. Zhong, C. Zhang, Y. He, and Z. Chen, ``A method for the estimation  of  the  battery  pack  state  of  charge  based  on  in-pack  cells  uniformityanalysis,”Applied Energy, vol. 113, pp. 558–564, 2014.
  
 \bibitem{ZS_shaheer} 
  Muhammad, Shaheer, et al. ``A Robust Algorithm for State-of-Charge Estimation with Gain Optimization.'' IEEE Transactions on Industrial Informatics (2017).
  
  \bibitem{ZS_coi}
  https://www.coilwindingexpo.com/berlin/design-and-test-perfect-the-electric-vehicle-balancing-act
  
  \bibitem{ZS_war}
  R. A. Waraich, M. Galus, C. Dobler, M. Balmer, G. Andersson, and K.
Axhausen, ``Plug-in hybrid electric vehicles and smart grid: Investigations
based on a micro-simulation,” Institute for Transport Planning
and Systems, ETH Zurich, Switzerland, Tech. Rep. 10.3929/ethz-a-
005916811, 2009.

\bibitem{ZS_rah}
S. Rahman and Y. Teklu, ``Role of the electric vehicle as a distributed
resource,” in Proc. IEEE Power Eng. Soc. Winter Meet., Singapore,
Jan. 23–27, 2000, vol. 1, pp. 528–533.

\bibitem{ZS_gal}
 M. D. Galus and G. Andersson, ``Demand management of grid connected
plug-in hybrid electric vehicles (PHEV),” in Proc. IEEE Energy
2030 Conf., Atlanta, GA, Nov. 17–18, 2008, pp. 1–8.

\bibitem{ZS_sun}
Sundstrom, Olle, and Carl Binding., ``Flexible charging optimization for electric vehicles considering distribution grid constraints.'' IEEE Transactions on Smart Grid 3.1 (2012): 26-37.

\bibitem{ZS_sun2}
Sundstrom, Olle, and Carl Binding. ``Optimization methods to plan the charging of electric vehicle fleets.'' Proceedings of the international conference on control, communication and power engineering. 2010.

\bibitem{ZS_salameh}
Salameh, Ziyad M., Margaret A. Casacca, and William A. Lynch. ``A mathematical model for lead-acid batteries.'' IEEE Transactions on Energy Conversion 7.1 (1992): 93-98.

