
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Electric vehicles have many fundamental advantages over internal combustion engine vehicles. Electric vehicle idea was not new. As early as in 1891, William Morrison of Des Moines, Iowa already built the first successful electric vehicle in the United States. However, internal combustion engines almost completely replaced electric powertrains in the production vehicles for the past 100 years. 

Thanks to recent evolution of Lithium-ion batteries and strong demand for zero-emission vehicles, electric vehicles have successfully repositioned demonstrating commercial success. Nevertheless, electric vehicles still have challenges in terms of the battery weight, fully-charged driving range, costs, etc. In this survey, we would like to provide range of information toward “low-power” electric vehicles that is able to inspire how design automation can overcome such primary electric vehicles’ disadvantages more systematically and more efficiently. 

We first introduce propulsion power modeling, estimation, runtime optimization, and design-time optimization in Section~\ref{sec:propulsion} as majority of battery energy in the electric vehicles is used for propulsion. Section~\ref{sec:driving_profile} introduces driving profile modeling, estimation and runtime optimization on the top of Section~\ref{sec:propulsion}. Driving profile also largely impacts on non-propulsion power consumption. Indeed, modern electric vehicles also consume significant amount of battery energy for non-propulsion power such as heating, ventilation, and air conditioning (HVAC.) As battery systems are the key component for electric vehicles, we introduce modelling, simulation, estimation and optimization of electric vehicle batteries in Section~\ref{sec:battery} based on different energy sources, including solar energy, wind energy, regenerative shock absorbers, braking and waste heat recovery. Energy harvesting, as a promising renewable energy technique in EVs attracts many attentions in studying range extension, energy management and optimization, and the improvement of energy conversion efficiency. The peak load demand by electric vehicle charging activities causes significant stress on a power grid. Section~\ref{sec:power_grid} introduces modeling, simulation and optimization of electric vehicle charging and discharging on the power grid.


