\bibitem{JX_fthenakis2009technical}
V.~Fthenakis, J.~E. Mason, and K.~Zweibel,
\newblock ``The technical, geographical, and economic feasibility for solar
  energy to supply the energy needs of the us,''
\newblock Energy Policy 37(2):387--399, 2009.

\bibitem{JX_singh2012study}
R.~Singh, M.~K. Gaur, and C.~S. Malvi,
\newblock ``Study of solar energy operated hybrid mild cars: A review,''
\newblock International Journal of Scientific Engineering and Technology
  1(4):139--148, 2012.

\bibitem{JX_bourgeois2015harvesting}
J.~Bourgeois, S.~Foell, G.~Kortuem, B.~A. Price, J.~Van Der~Linden, E.~Y. Elbanhawy, and C.~Rimmer,
\newblock ``Harvesting green miles from my roof: an investigation into
  self-sufficient mobility with electric vehicles,''
\newblock In Proceedings of the 2015 ACM International Joint Conference on Pervasive and Ubiquitous Computing pages 1065--1076. ACM, 2015.

\bibitem{JX_wang2012dynamic}
Y.~Wang, X.~Lin, N.~Chang, and M.~Pedram,
\newblock ``Dynamic reconfiguration of photovoltaic energy harvesting system in
  hybrid electric vehicles,''
\newblock In Proceedings of the 2012 ACM/IEEE international symposium on
  Low power electronics and design pages 109--114. ACM, 2012.

\bibitem{JX_kim2014fast}
J.~Kim, Y.~Wang, M.~Pedram, and N.~Chang,
\newblock ``Fast photovoltaic array reconfiguration for partial solar powered
  vehicles,''
\newblock In Proceedings of the 2014 international symposium on Low power
  electronics and design pages 357--362. ACM, 2014.
  
\bibitem{JX_liu2008variable}
F.~Liu, S.~Duan, F.~Liu, B.~Liu, and Y.~Kang,
\newblock ``A variable step size inc mppt method for pv systems,''
\newblock IEEE Transactions on industrial electronics 55(7):2622--2628,
  2008.
  
\bibitem{JX_arsie2006hybrid}
I.~Arsie, M.~Cacciato, A.~Consoli, G.~Petrone, G.~Rizzo, M.~Sorrentino, and G.~Spagnuolo,
\newblock ``Hybrid vehicles and solar energy: a possible marriage?,''
\newblock ICAT06, Istanbul, November 17, 2006.
  
\bibitem{JX_ma2009research}
X.~Ma, Y.~Sun, J.~Wu, and S.~Liu,
\newblock ``The research on the algorithm of maximum power point tracking in photo voltaic array of solar car,''
\newblock In Vehicle Power and Propulsion Conference, 2009. VPPC'09.
  IEEE pages 1379--1382. IEEE, 2009.
 
\bibitem{JX_rajan2017solar}
N.~A. Rajan, K.~D. Shrikant, B.~Dhanalakshmi, and N.~Rajasekar,
\newblock ``Solar pv array reconfiguration using the concept of standard
  deviation and genetic algorithm,''
\newblock Energy Procedia 117:1062--1069, 2017.
  
\bibitem{JX_storey2014optimized}
J.~Storey, P.~R. Wilson, and D.~Bagnall,
\newblock ``The optimized-string dynamic photovoltaic array,''
\newblock IEEE Transactions on Power Electronics 29(4):1768--1776, 2014.
  
\bibitem{JX_arsie2006optimal}
I.~Arsie, G.~Rizzo, and M.~Sorrentino,
\newblock ``Optimal design and dynamic simulation of a hybrid solar vehicle,''
\newblock Technical report, SAE Technical Paper, 2006.
  
\bibitem{JX_vicente2015photovoltaic}
P.~d.~S. Vicente, T.~C. Pimenta, and E.~R. Ribeiro,
\newblock ``Photovoltaic array reconfiguration strategy for maximization of
  energy production,''
\newblock International Journal of Photoenergy 2015, 2015.

\bibitem{JX_vincent2013advanced}
V.~V. Vincent and S.~Kamalakkannan,
\newblock ``Advanced hybrid system for solar car,''
\newblock In Computation of Power, Energy, Information and Communication
  (ICCPEIC), 2013 International Conference on pages 21--27. IEEE, 2013.

\bibitem{JX_hopkins2015high}
A.~Hopkins, N.~McNeill, P.~Anthony, and P.~Mellor,
\newblock ``High efficiency bidirectional 5kw dc-dc converter with super-junction
  mosfets for electric vehicle super-capacitor systems,''
\newblock In Energy Conversion Congress and Exposition (ECCE), 2015 IEEE
  pages 4632--4639. IEEE, 2015.

\bibitem{JX_agrawal2016multi}
S.~Agrawal and S.~Singh,
\newblock ``Multi-port converter for solar powered hybrid vehicle,''
\newblock In Photovoltaic Specialists Conference (PVSC), 2016 IEEE 43rd
  pages 3258--3262. IEEE, 2016.

\bibitem{JX_chen2013green}
Y.-S. Chen, Y.-W. Lin, and C.-H. Wang,
\newblock ``A green time-bounded routing protocol in solar-based vehicular networks,''
\newblock In Innovative Mobile and Internet Services in Ubiquitous
  Computing (IMIS), 2013 Seventh International Conference on pages 336--341, 2013.

\bibitem{JX_aqeel2016optimized}
S.~S. Aqeel and N.~E. Elizabeth,
\newblock ``An optimized time bounded routing on solar based vehicuar ad-hoc networks using particle swarm optimization,''
\newblock In Intelligent Systems and Control (ISCO), 2016 10th International Conference on pages 1--5. IEEE, 2016.

\bibitem{JX_elizabeth2016velocity}
E.~N. Elizabeth and S.~A. Shahul,
\newblock ``Velocity Optimized Solar-Time bound Traffic free Routing (VOSTTR) EE Protocol for VANET's,''
\newblock International Journal of Computer Science and Information
  Security 14(12):438, 2016.
  
\bibitem{JX_lv2016speed}
M.~Lv, N.~Guan, Y.~Ma, D.~Ji, E.~Knippel, X.~Liu, and W.~Yi,
\newblock ``Speed planning for solar-powered electric vehicles,''
\newblock In Proceedings of the Seventh International Conference on Future Energy Systems page~6. ACM, 2016.  

\bibitem{JX_abdin2013solar}
Z.~Abdin, M.~Alim, R.~Saidur, M.~Islam, W.~Rashmi, S.~Mekhilef, and A.~Wadi,
\newblock ``Solar energy harvesting with the application of nanotechnology,''
\newblock Renewable and sustainable energy reviews 26:837--852, 2013.

\bibitem{JX_ZHANG2016177}
Z.~Zhang, X.~Zhang, W.~Chen, Y.~Rasim, W.~Salman, H.~Pan, Y.~Yuan, and C.~Wang,
\newblock ``A high-efficiency energy regenerative shock absorber using
  supercapacitors for renewable energy applications in range extended electric vehicle,''
\newblock Applied Energy 178(Supplement C):177 -- 188, 2016.

\bibitem{JX_ref1}
L.~Segel and X.~Lu,
\newblock ``Vehicular resistance to motion as influenced by road roughness and highway alignment,''
\newblock Australian road research 12(4):211--222, 1982.

\bibitem{JX_JOUR}
L.~Zuo and P.-S. Zhang,
\newblock ``Energy harvesting, ride comfort, and road handling of regenerative vehicle suspensions,''
\newblock volume 135, page~8, February 2013.

\bibitem{JX_HUANG201516}
B.~Huang, C.-Y. Hsieh, F.~Golnaraghi, and M.~Moallem,
\newblock ``Development and optimization of an energy-regenerative suspension
  system under stochastic road excitation,''
\newblock Journal of Sound and Vibration 357(Supplement C):16 -- 34,
  2015.

\bibitem{JX_0964-1726-19-4-045003}
L.~Zuo, B.~Scully, J.~Shestani, and Y.~Zhou,
\newblock ``Design and characterization of an electromagnetic energy harvester for vehicle suspensions,''
\newblock Smart Materials and Structures 19(4):045003, 2010.

\bibitem{JX_5737802}
B.~L.~J. Gysen, T.~P.~J. van~der Sande, J.~J.~H. Paulides, and E.~A. Lomonova,
\newblock ``Efficiency of a regenerative direct-drive electromagnetic active
  suspension,''
\newblock IEEE Transactions on Vehicular Technology 60(4):1384--1393,
  May 2011.

\bibitem{JX_ZHANG20121124}
G.~Zhang, J.~Cao, and F.~Yu,
\newblock ``Design of active and energy-regenerative controllers for
  dc-motor-based suspension,''
\newblock Mechatronics 22(8):1124 -- 1134, 2012.

\bibitem{JX_2619394820151001}
P.~Khaokhajorn, S.~Samipak, S.~Nithithanasilp, M.~Tanticharoen, and
  A.~Amnuaykanjanasin,
\newblock ``Production and secretion of naphthoquinones is mediated by the MFS transporter MFS1 in the entomopathogenic fungus ophiocordyceps sp. bcc1869,''
\newblock World Journal Of Microbiology Biotechnology 31(10):1543 --
  1554, 2015.

\bibitem{JX_XIE2015385}
X.~Xie and Q.~Wang,
\newblock ``Energy harvesting from a vehicle suspension system,''
\newblock Energy 86(Supplement C):385 -- 392, 2015.

\bibitem{JX_6063995}
L.~Hao and C.~Namuduri,
\newblock ``Electromechanical regenerative actuator with fault tolerance
  capability for automotive chassis applications,''
\newblock In 2011 IEEE Energy Conversion Congress and Exposition pages 1750--1757, Sept 2011.

\bibitem{JX_6023317}
S.~Liu, H.~Wei, and W.~Wang,
\newblock ``Investigation on some key issues of regenerative damper with rotary motor for automobile suspension,''
\newblock In Proceedings of 2011 International Conference on Electronic
  Mechanical Engineering and Information Technology volume~3, pages
  1435--1439, Aug 2011.

\bibitem{JX_doi}
Z.~Fang, X.~Guo, L.~Xu, and H.~Zhang,
\newblock ``Experimental study of damping and energy regeneration characteristics of a hydraulic electromagnetic shock absorber,''
\newblock Advances in Mechanical Engineering 5:943528, 2013.

\bibitem{JX_ZHANG2015485}
Y.~Zhang, X.~Zhang, M.~Zhan, K.~Guo, F.~Zhao, and Z.~Liu,
\newblock ``Study on a novel hydraulic pumping regenerative suspension for vehicles,''
\newblock Journal of the Franklin Institute 352(2):485 -- 499, 2015.
\newblock Special Issue on Control and Estimation of Electrified vehicles.

\bibitem{JX_pub1643510}
N.~Amati, A.~Canova, F.~Cavalli, S.~Carabelli, A.~Festini, A.~Tonoli, and
  G.~Caviasso,
\newblock ``Electromagnetic shock absorbers for automotive suspensions:
  electromechanical design,''
\newblock In Titolo volume non avvalorato 2006.

\bibitem{JX_6587850}
R.~Sabzehgar, A.~Maravandi, and M.~Moallem,
\newblock ``Energy regenerative suspension using an algebraic screw linkage mechanism,''
\newblock IEEE/ASME Transactions on Mechatronics 19(4):1251--1259, Aug 2014.
  
\bibitem{JX_7057652}
A.~Maravandi and M.~Moallem,
\newblock ``Regenerative shock absorber using a two-leg motion conversion mechanism,''
\newblock IEEE/ASME Transactions on Mechatronics 20(6):2853--2861, Dec 2015.  

\bibitem{JX_Gupta2006}
A.~Gupta, J.~A. Jendrzejczyk, T.~M. Mulcahy, and J.~R. Hull,
\newblock ``Design of electromagnetic shock absorbers,''
\newblock International Journal of Mechanics and Materials in Design
  3(3):285--291, Sep 2006.

\bibitem{JX_5545646}
P.~Li and L.~Zuo,
\newblock ``Equivalent circuit modeling of vehicle dynamics with regenerative shock absorbers,''
\newblock International Design Engineering Technical Conferences and
  Computers and Information in Engineering Conference 1, 2013.

\bibitem{JX_6399623}
Z.~Li, L.~Zuo, G.~Luhrs, L.~Lin, and Y.~x.~Qin,
\newblock ``Electromagnetic energy-harvesting shock absorbers: Design, modeling, and road tests,''
\newblock IEEE Transactions on Vehicular Technology 62(3):1065--1074,
  March 2013.

\bibitem{JX_0964}
Z.~Li, L.~Zuo, J.~Kuang, and G.~Luhrs,
\newblock ``Energy-harvesting shock absorber with a mechanical motion rectifier,''
\newblock Smart Materials and Structures 22(2):025008, 2013.

\bibitem{JX_regen_fig}
Christopher Lampton,
\newblock ``How Regenerative Braking Works,''
\newblock HowStuffWorks.com, 23, February, 2018, 
\newblock [Online]. Available: https://auto.howstuffworks.com/auto-parts/brakes/brake-types/regenerative-braking.htm.

\bibitem{JX_4450599}
S.~M. Lukic, J.~Cao, R.~C. Bansal, F.~Rodriguez, and A.~Emadi,
\newblock ``Energy storage systems for automotive applications,''
\newblock IEEE Transactions on Industrial Electronics 55(6):2258--2267,
  June 2008.

\bibitem{JX_4677669}
J.~Cao, N.~Schofield, and A.~Emadi,
\newblock ``Battery balancing methods: A comprehensive review,''
\newblock In 2008 IEEE Vehicle Power and Propulsion Conference pages
  1--6, Sept 2008.

\bibitem{JX_5764539}
J.~Cao and A.~Emadi,
\newblock ``A new battery/ultracapacitor hybrid energy storage system for
  electric, hybrid, and plug-in hybrid electric vehicles,''
\newblock IEEE Transactions on Power Electronics 27(1):122--132, Jan
  2012.

\bibitem{JX_5446335}
A.~Khaligh and Z.~Li,
\newblock ``Battery, ultracapacitor, fuel cell, and hybrid energy storage systems for electric, hybrid electric, fuel cell, and plug-in hybrid electric
  vehicles: State of the art,''
\newblock IEEE Transactions on Vehicular Technology 59(6):2806--2814,
  July 2010.

\bibitem{JX_DATE}
D.~MacKay,
\newblock ``Sustainable energy - without the hot air,''
\newblock Design and Technology Education: an International Journal
  16(1), 2011.

\bibitem{JX_Tie2013}
S.~F. Tie and C.~W. Tan,
\newblock ``A review of energy sources and energy management system in electric vehicles,''
\newblock Renewable and Sustainable Energy Reviews 20(Complete):82--102, 2013.

\bibitem{JX_2002013128}
R.~P. Kepner,
\newblock ``Hydraulic power assist ? a demonstration of hydraulic hybrid vehicle
  regenerative braking in a road vehicle application,''
\newblock Portugal: Polytechnic Institute of Porto (IPP) page~8, 11
  2002.

\bibitem{JX_2008valents}
V.~S and F.~H,
\newblock ``Braking energy regeneration using hydraulic systems,''
\newblock Portugal: Polytechnic Institute of Porto (IPP) page~8, 2008.

\bibitem{JX_5472647}
J.~Dixon,
\newblock ``Energy storage for electric vehicles,''
\newblock In 2010 IEEE International Conference on Industrial Technology
  pages 20--26, March 2010.

\bibitem{JX_5686984}
M.~K. Yoong, Y.~H. Gan, G.~D. Gan, C.~K. Leong, Z.~Y. Phuan, B.~K. Cheah, and K.~W. Chew,
\newblock ``Studies of regenerative braking in electric vehicle,''
\newblock In 2010 IEEE Conference on Sustainable Utilization and
  Development in Engineering and Technology pages 40--45, Nov 2010.

\bibitem{JX_993788}
R.~Hebner, J.~Beno, and A.~Walls,
\newblock ``Flywheel batteries come around again,''
\newblock IEEE Spectrum 39(4):46--51, Apr 2002.










%
%
%\bibitem{JX_DEBATTISTA2006478}
%H.~D. Battista, R.~J. Mantz, and F.~Garelli,
%\newblock ``Power conditioning for a wind®chydrogen energy system,''
%\newblock Journal of Power Sources 155(2):478 -- 486, 2006.
%
%\bibitem{JX_BECHRAKIS200646}
%D.~Bechrakis, E.~McKeogh, and P.~Gallagher,
%\newblock ``Simulation and operational assessment for a small autonomous
%  wind®chydrogen energy system,''
%\newblock Energy Conversion and Management 47(1):46 -- 59, 2006.
%
%\bibitem{JX_7006196}
%C.~Chellaswamy and R.~Ramesh,
%\newblock ``Green energy harvesting: Recharging electric vehicle for pollution
%  free environment,''
%\newblock In 2014 International Conference on Smart Structures and Systems
%  (ICSSS) pages 59--66, Oct 2014.
%
%
%
%\bibitem{JX_1304613}
%B.~Delfino and F.~Fornari,
%\newblock ``Modeling and control of an integrated fuel cell-wind turbine system,''
%\newblock In 2003 IEEE Bologna Power Tech Conference Proceedings,
%  volume~2, pages 6 pp. Vol.2--, June 2003.
%
%\bibitem{JX_doi528}
%Z.~Fang, X.~Guo, L.~Xu, and H.~Zhang.
%\newblock Experimental study of damping and energy regeneration characteristics
%  of a hydraulic electromagnetic shock absorber.
%\newblock Advances in Mechanical Engineering 5:943528, 2013.
%
%\bibitem{JX_KHAN2005421}
%M.~Khan and M.~Iqbal,
%\newblock ``Dynamic modeling and simulation of a small wind®cfuel cell hybrid
%  energy system,''
%\newblock Renewable Energy 30(3):421 -- 439, 2005.
%
%%
%\bibitem{JX_Moshfegh}
%B.~Moshfegh,
%\newblock ``World renewable energy congress - sweden; 8-13 may; 2011; link\"{o}ping;
%  sweden,''
%\newblock In World Renewable Energy Congress - Sweden; 8-13 May; 2011;
%  Link\"{o}ping; Sweden volume~10. Link\"{o}ping University Electronic Press;
%  Link\"{o}pings universitet, 2011.
%
%\bibitem{JX_7925346}
%T.~Moustafa and W.~Moreno,
%\newblock ``Ram air and wind energy harvesting survey for electrical vehicles and
%  transportation,''
%\newblock In SoutheastCon 2017 pages 1--7, March 2017.
%
%\bibitem{JX_8077284}
%N.~K. Navin and R.~Sharma,
%\newblock ``A modified differential evolution approach to phev integrated thermal
%  unit commitment proble,''
%\newblock In 2016 IEEE 7th Power India International Conference (PIICON)
%  pages 1--4, Nov 2016.
%
%\bibitem{JX_ONAR2006707}
%O.~Onar, M.~Uzunoglu, and M.~Alam,
%\newblock ``Dynamic modeling, design and simulation of a wind/fuel
%  cell/ultra-capacitor-based hybrid power generation system,''
%\newblock Journal of Power Sources 161(1):707 -- 722, 2006.
%
%\bibitem{JX_4762597}
%T.~Senjyu, S.~Chakraborty, A.~Y. Saber, H.~Toyama, A.~Yona, and T.~Funabashi,
%\newblock ``Thermal unit commitment strategy with solar and wind energy systems
%  using genetic algorithm operated particle swarm optimization,''
%\newblock In 2008 IEEE 2nd International Power and Energy Conference
%  pages 866--871, Dec 2008.
%
%\bibitem{JX_6183172}
%Y.~Zhang, W.~Wang, Y.~Kobayashi, and K.~Shirai,
%\newblock ``Remaining driving range estimation of electric vehicle,''
%\newblock In 2012 IEEE International Electric Vehicle Conference pages
%  1--7, March 2012.




