

\bibitem{AF_1}
K. Vatanparvar and M. A. Al Faruque, “Eco-Friendly Automotive Climate Control and Navigation System for Electric Vehicles,” in 2016 ACM/IEEE 7th International Conference on Cyber-Physical Systems, ICCPS 2016 - Proceedings, 2016.

\bibitem{AF_2}
M. Lukasiewycz et al., “System architecture and software design for electric vehicles,” in Proceedings - Design Automation Conference, 2013.

\bibitem{AF_3}
R. C. Hsu, C. T. Liu, and D. Y. Chan, “A reinforcement-learning-based assisted power management with QoR provisioning for human-electric hybrid bicycle,” IEEE Trans. Ind. Electron., vol. 59, pp. 3350–3359, 2012.

%\bibitem{AF_4}
%S. Park, Y. Kim, and N. Chang, “Hybrid Energy Storage Systems and Battery Management for Electric Vehicles,” in DAC ’13 Proceedings of the 50th Annual Design Automation Conference, 2013, pp. 1–6.

\bibitem{AF_5}
E. Kim, J. Lee, and K. G. Shin, “Real-time prediction of battery power requirements for electric vehicles,” in 2013 ACM/IEEE International Conference on Cyber-Physical Systems, ICCPS 2013, 2013, pp. 11–20.

\bibitem{AF_6}
J. G. Hayes, R. P. R. De Oliveira, S. Vaughan, and M. G. Egan, “Simplified Electric Vehicle Power Train Models and Range Estimation,” IEEE Veh. Power Propuls. Conf., pp. 1–5, 2011.

\bibitem{AF_7}
S. R. Cikanek and K. E. Bailey, “Regenerative braking system for a hybrid electric vehicle,”Control Conf. (IEEE Cat. No.CH37301), vol. 4, pp. 3129–3134, 2002.

\bibitem{AF_8}
K. Vatanparvar and M. A. Al Faruque, “OTEM: Optimized Thermal and Energy Management for Hybrid Electrical Energy Storage in Electric Vehicles,” Conf. Des. Autom. Test Eur., pp. 1–6, 2016.

\bibitem{AF_9}
A. Emadi, Young Joo Lee, and K. Rajashekara, “Power Electronics and Motor Drives in Electric, Hybrid Electric, and Plug-In Hybrid Electric Vehicles,” IEEE Trans. Ind. Electron., vol. 55, no. 6, pp. 2237–2245, 2008.

\bibitem{AF_10}
K. Vatanparvar and M. A. Al Faruque, “Battery Lifetime-Aware Automotive Climate Control for Electric Vehicles,” ACM/IEEE Des. Autom. Conf., pp. 1–6, 2015.	

\bibitem{AF_11}
K. Vatanparvar and M. A. Al Faruque, “Electric Vehicle Optimized Charge and Drive Management,” ACM Trans. Des. Autom. Electron. Syst., vol. 23, no. 1, p. 3:1--3:25, Aug. 2017.

%\bibitem{AF_12}
%K. Vatanparvar and M. A. Al Faruque, “Battery Lifetime-Aware Automotive Climate Control for Electric Vehicles,” in ACM/IEEE Design Automation Conference (DAC’15), 2015, pp. 1–6.

\bibitem{AF_13}
A. Kelman and F. Borrelli, “Bilinear Model Predictive Control of a HVAC System Using Sequential Quadratic Programming,” in International Federation of Automatic Control World Congress, 2011, pp. 9869–9874.

\bibitem{AF_14}
K. R. Kambly and T. H. Bradley, “Estimating the HVAC energy consumption of plug-in electric vehicles,” J. Power Sources, vol. 259, pp. 117–124, 2014.

\bibitem{AF_15}
R. Montgomery, “Fundamentals of HVAC control systems,” Elsevier, 2008.

\bibitem{AF_16}
B. Tashtoush, M. Molhim, and M. Al-Rousan, “Dynamic model of an HVAC system for control analysis,” Energy, vol. 30, pp. 1729–1745, 2005.

\bibitem{AF_17}
K. Vatanparvar, J. Wan, and M. A. Al Faruque, “Battery-aware energy-optimal Electric Vehicle driving management,” in Proceedings of the International Symposium on Low Power Electronics and Design, 2015, vol. 2015–Septe, pp. 353–358.

\bibitem{AF_18}
P. Baltusis, “On-board vehicle diagnostics,” Converg. Transp. Electron. Assoc., p. 15, 2004.

\bibitem{AF_19}
A. Wahab, C. Quek, C. K. Tan, and K. Takeda, “Driving profile modeling and recognition based on soft computing approach.,” IEEE Trans. Neural Netw., vol. 20, no. 4, pp. 563–582, 2009.

\bibitem{AF_20}
A. Ryguła, “Driving style identification method based on speed graph analysis,” in Proceedings - 2009 International Conference on Biometrics and Kansei Engineering, ICBAKE 2009, 2009, pp. 76–79.

\bibitem{AF_21}
E. Berdoulat, D. Vavassori, and M. T. M. Sastre, “Driving anger, emotional and instrumental aggressiveness, and impulsiveness in the prediction of aggressive and transgressive driving,” Accid. Anal. Prev., vol. 50, pp. 758–767, 2013.

\bibitem{AF_22}
A. B. Rodriguez Gonzalez, M. R. Wilby, J. J. Vinagre Diaz, and C. Sanchez Avila, “Modeling and detecting aggressiveness from driving signals,” IEEE Trans. Intell. Transp. Syst., vol. 15, no. 4, pp. 1419–1428, 2014.

\bibitem{AF_23}
J. Neubauer and E. Wood, “Thru-life impacts of driver aggression, climate, cabin thermal management, and battery thermal management on battery electric vehicle utility,” J. Power Sources, vol. 259, pp. 262–275, 2014.

\bibitem{AF_24}
J. A. Groeger and J. A. Rothengatter, “Traffic psychology and behaviour,” Transp. Res. Part F Traffic Psychol. Behav., vol. 1, no. 1, pp. 1–9, 1998.

\bibitem{AF_25}
Google Inc., “The Google Directions API.” [Online]. Available: developers.google.com/maps/documentation/directions. [Accessed: 01-Jan-2014].

\bibitem{AF_26}
E. Tzirakis, K. Pitsas, F. Zannikos, and S. Stournas, “Vehicle Emissions and Driving Cycles: Comparison of the Athens Driving Cycle (Adc) with Ece-15 and European Driving Cycle (Edc),” Glob. NEST J., vol. 8, no. 3, pp. 282–290, 2006.

\bibitem{AF_27}
G. Fontaras, P. Pistikopoulos, and Z. Samaras, “Experimental evaluation of hybrid vehicle fuel economy and pollutant emissions over real-world simulation driving cycles,” Atmos. Environ., vol. 42, no. 18, pp. 4023–4035, 2008.

\bibitem{AF_28}
K. Kambly and T. H. Bradley, “Geographical and temporal differences in electric vehicle range due to cabin conditioning energy consumption,” J. Power Sources, vol. 275, pp. 468–475, 2015.

\bibitem{AF_29}
M. A. Al Faruque and K. Vatanparvar, “HVAC System and Automotive Climate Control Influence on Electric Vehicle and Battery,” Asia South Pacific Des. Autom. Conf., pp. 1–6, 2016.

\bibitem{AF_30}
K. D. Huang, S. C. Tzeng, T. M. Jeng, and W. D. Chiang, “Air-conditioning system of an intelligent vehicle-cabin,” Appl. Energy, vol. 83, pp. 545–557, 2006.

\bibitem{AF_31}
S. Daly, Automotive air condiotining and climate control systems, no. 1. 2006.

\bibitem{AF_32}
	D. Mihai, “Fuzzy control for temperature of the driver seat in a car,” in 2012 International Conference on Applied and Theoretical Electricity, ICATE 2012 - Proceedings, 2012.

\bibitem{AF_33}
	B. S. K. K. Ibrahim et al., “Fuzzy-based Temperature and Humidity Control for HV AC of Electric Vehicle,” Procedia Engineering, vol. 41. pp. 904–910, 2012.

\bibitem{AF_34}
	E. F. Camacho and C. B. Alba, Model predictive control. Springer Science \& Business Media, 2013.

\bibitem{AF_35}
	S. T. Cheng, J. S. Shih, and T. Y. Chang, “GA-based actuator control method for minimizing power consumption in cyber physical systems,” Appl. Intell., vol. 38, no. 1, pp. 78–87, 2013.

\bibitem{AF_36}
	Y. Wang, Y. Kim, Q. Xie, N. Chang, and M. Pedram, “Charge migration efficiency optimization in hybrid electrical energy storage (HEES) systems,” in Proceedings of the International Symposium on Low Power Electronics and Design, 2011, pp. 103–108.

\bibitem{AF_37}
	C. Warren, “Fast Path Planning Using Modified A * Method,” Robot. Autom. 1993. Proceedings., 1993 IEEE Int. Conf., pp. 662–667, 1993.

\bibitem{AF_38}
	H. Gonzalez, J. Han, and X. Li, “Adaptive fastest path computation on a road network: A traffic mining approach,” Proc. 33rd VLDB, pp. 794–805, 2007.

\bibitem{AF_39}
	I. Chabini and S. Lan, “Adaptations of the A* Algorithm for the Computation of Fastest Paths in Deterministic Discrete-Time Dynamic Networks,” IEEE Trans. Intell. Transp. Syst., vol. 3, no. 1, pp. 60–74, 2002.


\bibitem{AF_40}
	T. Wang, C. G. Cassandras, and S. Pourazarm, “Energy-aware Vehicle Routing in Networks with Charging Nodes,” 9th World Congr. Int. Fed. Autom. Control, pp. 1–9, 2014.


\bibitem{AF_41}
	Y. Wang, J. Jiang, and T. Mu, “Context-aware and energy-driven route optimization for fully electric vehicles via crowdsourcing,” IEEE Trans. Intell. Transp. Syst., vol. 14, pp. 1331–1345, 2013.


\bibitem{AF_42}
	J. Eisner, S. Funke, and S. Storandt, “Optimal Route Planning for Electric Vehicles in Large Networks.,” Aaai, pp. 1108–1113, 2011.


\bibitem{AF_43}
	M. HE, W. CAI, and S. LI, “Multiple fuzzy model-based temperature predictive control for HVAC systems,” Inf. Sci. (Ny)., vol. 169, no. 1–2, pp. 155–174, Jan. 2005.

