
\bibitem{YC_Hadley}
S.~W. Hadley, ``Impact of plug-in hybrid vehicles on the electric grid,''

\bibitem{YC_Putrus}
G.~A. Putrus, P.~Suwanapingkarl, D.~Johnston, E.~C. Bentley, and M.~Narayana,
  ``Impact of electric vehicles on power distribution networks,'' in 2009
  IEEE Vehicle Power and Propulsion Conference, pp.~827--831, Sept 2009.

\bibitem{YC_Clement}
K.~Clement-Nyns, E.~Haesen, and J.~Driesen, ``The impact of charging plug-in
  hybrid electric vehicles on a residential distribution grid,'' IEEE
  Transactions on Power Systems, vol.~25, pp.~371--380, Feb 2010.

\bibitem{YC_smartgrid1}
S.~Deilami, A.~S. Masoum, P.~S. Moses, and M.~A.~S. Masoum, ``Real-time
  coordination of plug-in electric vehicle charging in smart grids to minimize
  power losses and improve voltage profile,'' IEEE Transactions on Smart
  Grid, vol.~2, pp.~456--467, Sept 2011.

\bibitem{YC_smartgrid2}
K.~Clement-Nyns, E.~Haesen, and J.~Driesen, ``The impact of charging plug-in
  hybrid electric vehicles on a residential distribution grid,'' IEEE
  Transactions on Power Systems, vol.~25, pp.~371--380, Feb 2010.

\bibitem{YC_smartgrid}
H.~Farhangi, ``The path of the smart grid,'' IEEE Power and Energy
  Magazine, vol.~8, pp.~18--28, January 2010.

\bibitem{YC_Adornato10}
B.~Adornato, R.~Patil, Z.~Filipi, Z.~Baraket, and T.~Gordon, ``Characterizing
  naturalistic driving patterns for plug-in hybrid electric vehicle analysis,''
  in 2009 IEEE Vehicle Power and Propulsion Conference, pp.~655--660,
  Sept 2009.

\bibitem{YC_Ashtari11}
A.~Ashtari, E.~Bibeau, S.~Shahidinejad, and T.~Molinski, ``Pev charging profile
  prediction and analysis based on vehicle usage data,'' IEEE Transactions
  on Smart Grid, vol.~3, pp.~341--350, March 2012.

\bibitem{YC_Zhao12}
M.~Hübner, L.~Zhao, T.~Mirbach, H.~J. Haubrich, and A.~Moser, ``Impact of
  large-scale electric vehicle application on the power supply,'' in 2009
  IEEE Electrical Power Energy Conference (EPEC), pp.~1--6, Oct 2009.

\bibitem{YC_David}
D.~B. Richardson, ``Electric vehicles and the electric grid: A review of
  modeling approaches, impacts, and renewable energy integration,'' Renewable and Sustainable Energy Reviews, vol.~19, pp.~247 -- 254, 2013.

\bibitem{YC_Stochastic}
K.~Clement, E.~Haesen, and J.~Driesen, ``Stochastic analysis of the impact of
  plug-in hybrid electric vehicles on the distribution grid,'' in CIRED
  2009 - The 20th International Conference and Exhibition on Electricity
  Distribution - Part 2, pp.~1--1, June 2009.

\bibitem{YC_Fernandes}
C.~Fernandes, P.~Frias, and J.~M. Latorre,
``Impact of vehicle-to-grid on power system operation costs: The spanish case study,'' 
Applied Energy, vol.~96, pp.~194 -- 202, 2012.
\newblock Smart Grids.

\bibitem{YC_Green}
R.~C. Green, L.~Wang, and M.~Alam, ``The impact of plug-in hybrid electric
  vehicles on distribution networks: A review and outlook,'' Renewable and
  Sustainable Energy Reviews, vol.~15, no.~1, pp.~544 -- 553, 2011.

\bibitem{YC_Hadley18}
S.~W. Hadley and A.~A. Tsvetkova, ``Potential impacts of plug-in hybrid
  electric vehicles on regional power generation,'' The Electricity
  Journal, vol.~22, no.~10, pp.~56 -- 68, 2009.

\bibitem{YC_Letendre19}
S.~Letendre and R.~Watts, ``Plug-in hybrid electric vehicles and the vermont
  grid: A scoping analysis,'' 10 2007.

\bibitem{YC_Kintner20}
M.~Kintner-Meyer, K.~Schneider, and R.~G.~Pratt, ``Impacts assessment of
  plug-in hybrid vehicles on electric utilities and regional us power grids:
  Part 1: Technical analysis,'' 01 2007.

\bibitem{YC_Denholm21}
P.~Denholm and W.~Short, ``An evaluation of utility system impacts and benefits
  of optimally dispatched plug-in hybrid electric vehicles (revised),''

\bibitem{YC_Hajimiragha23}
A.~Hajimiragha, C.~A. Canizares, M.~W. Fowler, and A.~Elkamel, ``Optimal
  transition to plug-in hybrid electric vehicles in ontario, canada,
  considering the electricity-grid limitations,'' IEEE Transactions on
  Industrial Electronics, vol.~57, pp.~690--701, Feb 2010.

\bibitem{YC_Hajimiragha24}
A.~H. Hajimiragha, C.~A. Canizares, M.~W. Fowler, S.~Moazeni, and A.~Elkamel,
  ``A robust optimization approach for planning the transition to plug-in
  hybrid electric vehicles,'' IEEE Transactions on Power Systems,
  vol.~26, pp.~2264--2274, Nov 2011.

\bibitem{YC_Hartmann25}
N.~Hartmann and E.~Ozdemir, ``Impact of different utilization scenarios of
  electric vehicles on the german grid in 2030,'' Journal of Power
  Sources, vol.~196, no.~4, pp.~2311 -- 2318, 2011.

\bibitem{YC_Papadopoulos27}
P.~Papadopoulos, L.~M. Cipcigan, N.~Jenkins, and I.~Grau, ``Distribution
  networks with electric vehicles,'' in 2009 44th International
  Universities Power Engineering Conference (UPEC), pp.~1--5, Sept 2009.

\bibitem{YC_Richardson28}
P.~Richardson, D.~Flynn, and A.~Keane, ``Impact assessment of varying
  penetrations of electric vehicles on low voltage distribution systems,'' in
  IEEE PES General Meeting, pp.~1--6, July 2010.

\bibitem{YC_Gomez29}
J.~C. Gomez and M.~M. Morcos, ``Impact of ev battery chargers on the power
  quality of distribution systems,'' IEEE Transactions on Power Delivery,
  vol.~18, pp.~975--981, July 2003.

\bibitem{YC_Chan30}
M.~S.~W. Chan, K.~T. Chau, and C.~C. Chan, ``Modeling of electric vehicle
  chargers,'' in Industrial Electronics Society, 1998. IECON '98.
  Proceedings of the 24th Annual Conference of the IEEE, vol.~1, pp.~433--438
  vol.1, Aug 1998.

\bibitem{YC_Leite33}
A.~M.~L. da~Silva, J.~L. Jardim, A.~M. Rei, and J.~C.~O. Mello, ``Dynamic
  security risk assessment,'' in 1999 IEEE Power Engineering Society
  Summer Meeting. Conference Proceedings (Cat. No.99CH36364), vol.~1,
  pp.~198--205 vol.1, Jul 1999.

\bibitem{YC_Jian}
W.~Jian, L.~Zhizhen, W.~Kuihua, W.~Feng, and Z.~Yi, ``Impact of plug-in hybrid
  electric vehicles on power distribution networks,'' in 2011 4th
  International Conference on Electric Utility Deregulation and Restructuring
  and Power Technologies (DRPT), pp.~1618--1622, July 2011.

\bibitem{YC_Gong}
Q.~Gong, S.~Midlam-Mohler, V.~Marano, and G.~Rizzoni, ``Study of pev charging
  on residential distribution transformer life,'' IEEE Transactions on
  Smart Grid, vol.~3, pp.~404--412, March 2012.

\bibitem{YC_Papadopoulos}
P.~Papadopoulos, S.~Skarvelis-Kazakos, I.~Grau, L.~M. Cipcigan, and N.~Jenkins,
  ``Electric vehicles' impact on british distribution networks,'' IET
  Electrical Systems in Transportation, vol.~2, pp.~91--102, September 2012.

\bibitem{YC_Schneider}
K.~Schneider, C.~Gerkensmeyer, M.~Kintner-Meyer, and R.~Fletcher, ``Impact
  assessment of plug-in hybrid vehicles on pacific northwest distribution
  systems,'' in 2008 IEEE Power and Energy Society General Meeting -
  Conversion and Delivery of Electrical Energy in the 21st Century, pp.~1--6,
  July 2008.

\bibitem{YC_Roe}
C.~Roe, E.~Farantatos, J.~Meisel, A.~P. Meliopoulos, and T.~Overbye, ``Power
  system level impacts of phevs,'' in 2009 42nd Hawaii International
  Conference on System Sciences, pp.~1--10, Jan 2009.

\bibitem{YC_Clement09}
K.~Clement, E.~Haesen, and J.~Driesen, ``Coordinated charging of multiple
  plug-in hybrid electric vehicles in residential distribution grids,'' in
  2009 IEEE/PES Power Systems Conference and Exposition, pp.~1--7, March 2009.

\bibitem{YC_FORD1995207}
A.~Ford, ``The impacts of large scale use of electric vehicles in southern
  california,'' Energy and Buildings, vol.~22, no.~3, pp.~207 -- 218,
  1995.

\bibitem{YC_JUUL20113523}
N.~Juul and P.~Meibom, ``Optimal configuration of an integrated power and
  transport system,'' Energy, vol.~36, no.~5, pp.~3523 -- 3530, 2011.

\bibitem{YC_Sortomme}
E.~Sortomme, M.~M. Hindi, S.~D.~J. MacPherson, and S.~S. Venkata, ``Coordinated
  charging of plug-in hybrid electric vehicles to minimize distribution system
  losses,'' IEEE Transactions on Smart Grid, vol.~2, pp.~198--205, March
  2011.

\bibitem{YC_Acha}
S.~Acha, T.~C. Green, and N.~Shah, ``Effects of optimised plug-in hybrid
  vehicle charging strategies on electric distribution network losses,'' in
  IEEE PES T D 2010, pp.~1--6, April 2010.

\bibitem{YC_V2Gconcept1}
W.~Kempton and J.~Tomic, ``Vehicle-to-grid power fundamentals: Calculating
  capacity and net revenue,'' Journal of Power Sources, vol.~144, no.~1,
  pp.~268 -- 279, 2005.

\bibitem{YC_V2Gconcept2}
W.~Kempton and J.~Tomic, ``Vehicle-to-grid power implementation: From
  stabilizing the grid to supporting large-scale renewable energy,'' 
  Journal of Power Sources, vol.~144, no.~1, pp.~280 -- 294, 2005.

\bibitem{YC_Reid}
P.~Reid, C.~Mittelstadt, and T.~Faber, ``Electric vehicle conductive charge
  couplers,'' in 2014 IEEE 60th Holm Conference on Electrical Contacts
  (Holm), pp.~1--7, Oct 2014.

\bibitem{YC_Sutanto}
D.~Sutanto, ``Alternative energy resource from electric transportation,'' in
  Proceedings. 2004 First International Conference on Power Electronics
  Systems and Applications, 2004., pp.~149--154, Nov 2004.

\bibitem{YC_Brooks}
A.~Brooks, ``Integration of electric drive vehicles with the power grid-a new
  application for vehicle batteries,'' in Seventeenth Annual Battery
  Conference on Applications and Advances. Proceedings of Conference (Cat.
  No.02TH8576), pp.~239--, Jan 2002.

\bibitem{YC_newyork}
N.~Y. ISO, ``Alternate route: Electrifying the transportation sector,''
  New York ISO, Jun 2009.

\bibitem{YC_DRUITT2012104}
J.~Druitt and W.-G. Fruh, ``Simulation of demand management and grid
  balancing with electric vehicles,'' Journal of Power Sources, vol.~216,
  pp.~104 -- 116, 2012.